\chapter{Ethics Submission}

\textbf{Date:} 20th February 2020
\textbf{Reference:} 15221

\textbf{AU Status}

Undergraduate or PG Taught

\textbf{Your aber.ac.uk email address}

mim39@aber.ac.uk

\textbf{Full Name}

Michael Male

\textbf{Please enter the name of the person responsible for reviewing your assessment.}

Reyer Zwiggelaar

\textbf{Please enter the aber.ac.uk email address of the person responsible for reviewing your assessment}

rrz@aber.ac.uk

\textbf{Supervisor or Institute Director of Research Department}

cs

\textbf{Module code (Only enter if you have been asked to do so)}

CS39440

\textbf{Proposed Study Title}

Development of a map-based web application to be used by visitors and staff at the Dyfi
Wildlife Centre

\textbf{Proposed Start Date}

27 January 2020

\textbf{Proposed Completion Date}

1 June 2020

\textbf{Are you conducting a quantitative or qualitative research project?}

Mixed Methods

\textbf{Does your research require external ethical approval under the Health Research Authority?}

No

\textbf{Does your research involve animals?}

Yes

\textbf{Does your research involve human participants?}

Yes

\textbf{Are you completing this form for your own research?}

No

\textbf{Does your research involve human participants?}

Yes

\textbf{Institute}

IMPACS

\textbf{Please provide a brief summary of your project (150 word max)}

A web application that provides information about specific points of interest around the
Cors Dyfi Nature Reserve on a Google Maps API, with persistent data stored in a
PostgreSQL database. The application will be accessed on a computer based at the Dyfi
Wildlife Centre; its intention is for staff to more easily explain the work that the centre
carries out. Proposed data collection includes regular user experience surveys and
collaboration with staff at the Montgomeryshire Wildlife Trust regarding information
about the centre and local businesses/transport they wish to showcase. There has also
been a proposed task to include geospatial data from GNSS trackers that were placed on
western ospreys prior to the beginning of this project. The ospreys live at the nature
reserve and migrate to Africa during the winter.

\textbf{I can confirm that the study does not involve vulnerable participants including participants under the age of 18, those with learning/communication or associated difficulties or those that are otherwise unable to provide informed consent?}

Yes

\textbf{I can confirm that the participants will not be asked to take part in the study without their consent or knowledge at the time and participants will be fully informed of the purpose of the research (including what data will be gathered and how it shall be used during and after the study). Participants will also be given time to consider whether they wish to take part in the study and be given the right to  withdraw at any given time.}

Yes

\textbf{I can confirm that there is no risk that the nature of the research topic might lead to disclosures from the participant concerning their own involvement in illegal activities or other activities that represent a risk to themselves or others (e.g. sexual activity, drug use or professional misconduct).}

Yes

\textbf{I can confirm that the study will not induce stress, anxiety, lead to humiliation or cause harm or any other negative consequences beyond the risks encountered in the participant’s day-to-day lives.}

Yes

\textbf{Please include any further relevant information for this section here: Where appropriate, do you have consent for the publication, reproduction or use of any unpublished material?}

Not applicable

\textbf{Will appropriate measures be put in place for the secure and confidential storage of data?}

Yes

\textbf{Does the research pose more than minimal and predictable risk to the researcher?}

No

\textbf{Will you be travelling, as a foreign national, in to any areas that the UK Foreign and Commonwealth Office advise against travel to?}

No

\textbf{Please include any further relevant information for this section here: If you are to be working alone with vulnerable people or children, you may need a DBS (CRB) check. Tick to confirm that you will ensure you comply with this requirement should you identify that you require one.}

Yes

\textbf{Declaration: Please tick to confirm that you have completed this form to the best of your knowledge and that you will inform your department should the proposal significantly change.}

Yes

\textbf{Please include any further relevant information for this section here:}

N/A