\chapter{Background \& Objectives}

\section{Background}
What was your background preparation for the project? What similar systems did you assess? What was your motivation and interest in this project?

\section{Analysis}
Taking into account the problem and what you learned from the background work, what was your analysis of the problem? How did your analysis help to decompose the problem into the main tasks that you would undertake? Were there alternative approaches? Why did you choose one approach compared to the alternatives? 

There should be a clear statement of the objectives of the work, which you will evaluate at the end of the work. 

In most cases, the agreed objectives or requirements will be the result of a compromise between what would ideally have been produced and what was determined to be possible in the time available. A discussion of the process of arriving at the final list is usually appropriate.

As mentioned in the lectures, think about possible security issues for the project topic. Whilst these might not be relevant for all projects, do consider if there are relevant for your project. Where there are relevant security issues, discuss how they will this affect the work that you are doing. Carry forward this discussion into relevant areas for design, implementation and testing.

\section{Process}

\subsection{Methods evaluated}

The software development lifecycle was an important part of the project to assess. During the planning stages of the project, I performed an evaluation of different methodologies, deciding upon a variation of Extreme Programming. 

